---
title: "DGEobj"
author: "John R. Thompson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The DGEobj package implements an S3 class data object, the DGEobj, that represents an extension of the capabilties of the RangedSummarizedExperiment(RSE).  Both the DGEobj and the RSE object capture the raw data for a differential gene expression analysis, namely a counts matrix along with associated gene and sample annotation.  However, the DGEobj extends this concept to support capture of downstream data objects the capture the workflow of and analysis project.   The availability of a structured data object like the DGEobj enables programactic inspect of analysis results and thus enable, automation of higher level integrative analysis across multiple projects.   

The RSE object that inspired the DGEobj can capture as many assays as desired. An "assay" is defined as any matrix with n genes (rows) and m samples (columns).  Moreover, the RSE


## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
